Visualizing Algebraic Surfaces

### 2016-02-19 project/article/src/article.tex
added a front page image and def of projective space

@@

@@

@@

@@

We start our study of algebraic surfaces by looking at \emph{projective space}.
Quite informally, projective space formalizes the notion of parallell lines
intersecting at infinity. In order to get a better understanding of the general
projective space $\proj^n$ we will first construct the \emph{real projective
plane}\index{real projective plane} $\proj^2(\R)$. According to \cite{Wik16}
there are three equivalent definitions:

@@

>>>>

% image handling
\usepackage[]{graphicx}

@@

\begin{titlepage}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\linewidth]{../pictures/labs_septic.png}
\end{figure}

\end{titlepage}

@@

\tableofcontents

@@

We start our study of algebraic surfaces by looking at \emph{projective space}.
Quite informally, projective space formalizes the notion of parallell lines
intersecting at infinity. In order to get a better understanding of the general
projective space $\proj^n$ we will first construct the \emph{real projective
plane}\index{real projective plane} $\proj^2(\R)$.

\subsection{The real projective plane}
According to \cite{Wik16} there are three equivalent definitions:

@@

We can now take the notion of the projective plane and generalize to $n$
dimensions.
\subsection{Projective Space}
\label{sub:projective_space}

The general definition of projective $n$-space is completely anologous to the
definition of the projective plane, the set of lines in $\R^{n+1}$ passing
through the origin, however we include a formal definition for completeness.

\begin{defn}[The real projective space of dimension $n$]\index{projective space}
    Let $\sim$ be an equivalence relation on $\R^{n+1}\setminus \left\{ \left(
    0, \ldots, 0 \right) \right\}$ defined by
    \begin{equation}
        \notag
        \left( x_1, \ldots, x_{n+1} \right) \sim \left( x_1', \ldots, x_{n+1}' \right) 
        \iff \left( x_1, \ldots, x_{n+1} \right) = \lambda \left( x_1', \ldots, x_{n+1}' \right)
    \end{equation} 
    where $\lambda$ is some positive real number. We then denote the
    equivalence class of $\left( x_1, \ldots, x_{n+1} \right)$ by
    $\projp{x_1}{\ldots}{x_{n+1}}$ and define \emph{the real projective space
    of dimension $n$} as the set
    \begin{equation}
        \notag
        \proj^n(\R) = \left\{ \projp{x_1}{\ldots}{x_{n+1}} \mid \left( x_1, \ldots, x_{n+1} \right) \in \R^{n+1} \setminus \left\{ \left( 0, \ldots, 0 \right) \right\} \right\}.
    \end{equation}

\end{defn}
